Study of Higgs plus single top production using events with a same sign dimuon at the Large Hadron Collider

### 2019-11-25 tesis_hiram/Chapter3/chapter3.tex
b

%!TEX root =../thesis. Tex
%*******************************************************************************
%****************************** Third Chapter **********************************
%*******************************************************************************
\chapter{Event reconstruction and selection}
During the proton collision, many types of processes happen whose information is saved in the CMS data storage system. But the events are only saved if they fulfill certain conditions compatible with the signal. 
For the tH process, the search is based on the presence of a pair of muons with the same sign. The rest of the processes that also generate a pair of muons with the same sign will be considered backgrounds. 
\section{Signal Event Topology} 
In this search, top quark decays to $Wb$ and from the $W$ boson decays to a muon and a neutrino. The Higgs decays to a pair of opposite sign $W$ bosons, where one of the bosons can decay to a $\mu$ and its neutrino. $b$ quark creates a b-jet. This is the main process that generates events with two same sign muons. The tH process topology is shown in  figure \ref{jet}.
 Finally there is a forward quark jet (highest $\eta$ value) generated from the initial collision. Additional jets or leptons can be generated from the other $W$ boson.

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[scale=1]{Chapter1/jet.png}
		\caption[Topology of $tH$]{Topology of $tH$ process which generates two same sign muons, a forward jet and a b-jet.} 
		\label{jet}
	\end{figure}
%Quarks and gluons only exist in bound states. Because of it, we cannot isolate quarks except the top quark because of their decay times that don't form a bound state. When two quarks are separated, the strong force interacting between them increases. The energy transforms into quark anti-quark pairs. The hadronization results in a jet of particles. 
\begin{table}[ht]
	\caption[Expected number of events for $tH$ decay chain with 35.9 fb$^{-1}$ of integrated luminosity at center of mass energy of $\sqrt{s}$=13 TeV ]{Expected number of events for different $tH$ decay chains assuming integrated luminosity of 35.9 fb$^{-1}$. $l$ represents $\mu^{\pm},e^\pm, \tau^\pm$.}
	\begin{tabular}{|l|c|c|}
		\hline
		Decay chain & BR & Events\\
		\hline 
		\small{$tH \rightarrow$ $W^+bW^+ W^-$ $\rightarrow$ $\mu^+$ $\nu_\mu b$ $\mu^+\nu_\mu$ $q \bar{q}'$ } &\small{2.096 $\times$10$^{-3}$} & 1.173 \\
		\hline
		\small{$tH \rightarrow W$$^+ b$$W^+$ $W^-$ $\rightarrow$ $\mu^+\nu_\mu b$ $\mu^+\nu_\mu$ $l^- \bar{\nu_l}$ } &\small{3.37 $\times$ 10$^{-4}$} &0.899 \\
		\hline
		\small{$tH \rightarrow$ $W^+ b$ $\tau^+ \tau^-$ $\rightarrow$ $\mu^+ \nu_\mu b$ $ \mu^+ \nu_\mu \bar{\nu_\tau} l^-\bar{\nu_l} \nu_\tau$} &\small{3.637$\times$10$^{-4}$}&0.203 \\
		\hline
		\small{$tH \rightarrow$ $W^+ b$ $W^+ W^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu$ $q\bar{q}$ $\rightarrow$ $\mu^+ \nu_\mu$ $\bar{\nu_\tau}$ $\bar{\nu_\tau} b\mu^+ \nu_\mu$ $q \bar{q}$} &\small{1.890$\times$10$^{-4}$}&0.105 \\
		\hline
		\small{$tH \rightarrow W^+ b \tau^+ \tau^-$ $\rightarrow$ $\mu^+$ $\nu_\mu b$ $\nu_\tau$ $\mu^+$ $\nu_\mu \bar{\nu_\tau}$} $q \bar{q}$ &
		\small{1.681 $\times$10$^{-4}$} & 0.094 \\
		\hline
		\small{$tH \rightarrow W^+ b$ $W^+ W^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau} b \mu^+ \nu_\mu l^- \bar{\nu_l}$ $\rightarrow$ $\mu^+\nu_\mu$ $ \bar{\nu_\tau} \bar{\nu_\tau} b \mu^+ \nu_\mu l^- \bar{\nu_l}$} &\small{3.045$\times$10$^{-5}$}& 0.017\\
		\hline
		\small{$tH \rightarrow W^+ bZZ$ $\rightarrow$ $q \bar{q} bZZ$ $\rightarrow$ $q \bar{q} b \mu^+ \mu^- \mu^+ \mu^-$} & \small{1.966$\times$10$^{-5}$} &0.011\\
		\hline 
		\small{$tH \rightarrow$ $W^+ b$ $\tau^+ \tau^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu \bar{\nu_\tau} $ $q\bar{q}' \nu_\tau$ $\rightarrow$ $\mu^+ \nu_\mu \bar{\nu_\tau}\bar{\nu_\tau} b \mu^+ \nu_\mu \bar{\nu_\tau} $ $q\bar{q}' \nu_\tau$ } &\small{1.549 $\times$10$^{-5}$} & 0.008 \\
		\hline
	\end{tabular}
	\label{tdecay}
\end{table}

@@

\section{Event Selection}
In order to detect signal events and reject background, the following selections are applied, according to the CMS publication\cite{th1} 
\begin{itemize}
	\item The events must contain two muons with the same sign.
	\item Transverse momentum $p_{t}$ > 25 GeV for the highest $p_t$ muon and $p_{t}$ > 15 GeV for the lowest $p_t$ muon.
	\item A forward jet with $p_t$ > 40 GeV and $|\eta|$ > 2.4
	\item One or more b-tagged jets with $|\eta|$ < 2.4
\end{itemize}
%Also it is possible to obtain a study of three leptons, given the mentioned decays can produce them. 
The number of expected events after the event selection predicted by the Monte Carlo simulations used in the CMS publication are shown in table \ref{tth-table} which corresponds to a integrated luminosity of 35.9 fb$^{-1}$\cite{th1}.
The backgrounds with the most events are $t\bar{t} W^\pm$, $t\bar{t}Z$ and Fakes. For the SM signal $tH$, the number of expected events is 2.14, while for the inverted coupling scenario ($k_t=-1$) the cross section is enhanced by a factor of approximately 10. 
These event yields will be used to estimate the signal sensitivity. The yields include statistical uncertainties due to the  Monte Carlo (MC) samples and systematic uncertainties as described in table \ref{tth-table}.

@@

\pagebreak
%The fake rate corresponds to non-prompt leptons.% Non prompt leptons are leptons that passed the selection, and usually comes from decays from b-jets (hadronized quarks). But due to jet signature is reconstructed as leptons, some particular signatures or errors in reconstruction, passed as leptons and then they called fakes leptons. Rare SM is a group of other processes: t$\bar{t}$t$\bar{t}$,WWW,WWZ,WZZ,WW,$t$Zq. Due to low number of events, they grouped the events as one histogram. 
\section{Multivariable discriminant}
Due to small signal to background ratio caused by the small cross section of $tH$, a multivariable discriminant, which separates signal from backgrounds, is necessary to optimize the signal sensitivity. The multivariable discriminant is a Boosted Decision Tree (BDT) that takes a set of input features and splits input data recursively based on those features\cite{tmva}. The features can be a mix of categorical and continuous data.
The BDT training is performed using several event variables.

In this analysis, the BDT discriminant was trained to discriminate against $t\bar{t}V$ background, because this background is one of the largest backgrounds. The variables used for the BDT were the following:

>>>>

%!TEX root =../thesis. Tex
%*******************************************************************************
%****************************** Third Chapter **********************************
%*******************************************************************************
\chapter{Event reconstruction and selection}
During the proton collision, many types of processes happen whose information is saved in the CMS data storage system. But the events are only saved if they fulfill certain conditions compatible with the signal. 
For the tH process, the search is based on the presence of a pair of muons with the same sign. The rest of the processes that also generate a pair of muons with the same sign will be considered backgrounds. 
\section{Signal Event Topology} 
In this search, top quark decays to $Wb$ and from the $W$ boson decays to a muon and a neutrino. The Higgs decays to a pair of opposite sign $W$ bosons, where one of the bosons can decay to a $\mu$ and its neutrino. $b$ quark creates a b-jet. This is the main process that generates events with two same sign muons. The tH process topology is shown in  Figure \ref{jet}.
 Finally there is a forward quark jet (highest $\eta$ value) generated from the initial collision. Additional jets or leptons can be generated from the other $W$ boson.

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[scale=1.3]{Chapter1/jet.png}
		\caption[Topology of $tH$]{Topology of $tH$ process which generates two same sign muons, a forward jet and a b-jet.} 
		\label{jet}
	\end{figure}
%Quarks and gluons only exist in bound states. Because of it, we cannot isolate quarks except the top quark because of their decay times that don't form a bound state. When two quarks are separated, the strong force interacting between them increases. The energy transforms into quark anti-quark pairs. The hadronization results in a jet of particles. 
\begin{table}[ht]
	\caption[Expected number of events for $tH$ decay chain with 35.9 fb$^{-1}$ of integrated luminosity at center of mass energy of $\sqrt{s}$=13 TeV ]{Expected number of events for different $tH$ decay chains assuming integrated luminosity of 35.9 fb$^{-1}$. $l$ represents $\mu^{\pm},e^\pm, \tau^\pm$.}
	\begin{tabular}{|l|c|c|}
		\hline
		Decay chain & BR & Events\\
		\hline 
		\small{$tH \rightarrow$ $W^+bW^+ W^-$ $\rightarrow$ $\mu^+$ $\nu_\mu b$ $\mu^+\nu_\mu$ $q \bar{q}'$ } &\small{2.096 $\times$10$^{-3}$} & 1.173 \\
		\hline
		\small{$tH \rightarrow W$$^+ b$$W^+$ $W^-$ $\rightarrow$ $\mu^+\nu_\mu b$ $\mu^+\nu_\mu$ $l^- \bar{\nu_l}$ } &\small{3.37 $\times$ 10$^{-4}$} &0.899 \\
		\hline
		\small{$tH \rightarrow$ $W^+ b$ $\tau^+ \tau^-$ $\rightarrow$ $\mu^+ \nu_\mu b$ $ \mu^+ \nu_\mu \bar{\nu_\tau} l^-\bar{\nu_l} \nu_\tau$} &\small{3.637$\times$10$^{-4}$}&0.203 \\
		\hline
		\small{$tH \rightarrow$ $W^+ b$ $W^+ W^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu$ $q\bar{q}$ $\rightarrow$ $\mu^+ \nu_\mu$ $\bar{\nu_\tau}$ $\bar{\nu_\tau} b\mu^+ \nu_\mu$ $q \bar{q}$} &\small{1.890$\times$10$^{-4}$}&0.105 \\
		\hline
		\small{$tH \rightarrow W^+ b \tau^+ \tau^-$ $\rightarrow$ $\mu^+$ $\nu_\mu b$ $\nu_\tau$ $\mu^+$ $\nu_\mu \bar{\nu_\tau}$} $q \bar{q}$ &
		\small{1.681 $\times$10$^{-4}$} & 0.094 \\
		\hline
		\small{$tH \rightarrow W^+ b$ $W^+ W^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau} b \mu^+ \nu_\mu l^- \bar{\nu_l}$ $\rightarrow$ $\mu^+\nu_\mu$ $ \bar{\nu_\tau} \bar{\nu_\tau} b \mu^+ \nu_\mu l^- \bar{\nu_l}$} &\small{3.045$\times$10$^{-5}$}& 0.017\\
		\hline
		\small{$tH \rightarrow W^+ bZZ$ $\rightarrow$ $q \bar{q} bZZ$ $\rightarrow$ $q \bar{q} b \mu^+ \mu^- \mu^+ \mu^-$} & \small{1.966$\times$10$^{-5}$} &0.011\\
		\hline 
		\small{$tH \rightarrow$ $W^+ b$ $\tau^+ \tau^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu \bar{\nu_\tau} $ $q\bar{q}' \nu_\tau$ $\rightarrow$ $\mu^+ \nu_\mu \bar{\nu_\tau}\bar{\nu_\tau} b \mu^+ \nu_\mu \bar{\nu_\tau} $ $q\bar{q}' \nu_\tau$ } &\small{1.549 $\times$10$^{-5}$} & 0.008 \\
		\hline
	\end{tabular}
	\label{tdecay}
\end{table}

@@

\section{Event Selection}
In order to detect signal events and reject background, the following selections are applied, according to the CMS publication\cite{th1} 
\begin{itemize}
	\item The events must contain two muons with the same sign.
	\item Transverse momentum $p_{t}$ > 25 GeV for the highest $p_t$ muon and $p_{t}$ > 15 GeV for the lowest $p_t$ muon.
	\item A forward jet with $p_t$ > 40 GeV and $|\eta|$ > 2.4
	\item One or more b-tagged jets with $|\eta|$ < 2.4
\end{itemize}
%Also it is possible to obtain a study of three leptons, given the mentioned decays can produce them. 
The number of expected events after the event selection predicted by the Monte Carlo simulations used in the CMS publication are shown in Table \ref{tth-table} which corresponds to a integrated luminosity of 35.9 fb$^{-1}$\cite{th1}.
The backgrounds with the most events are $t\bar{t} W^\pm$, $t\bar{t}Z$ and Fakes. For the SM signal $tH$, the number of expected events is 2.14, while for the inverted coupling scenario ($k_t=-1$) the cross section is enhanced by a factor of approximately 10. 
These event yields will be used to estimate the signal sensitivity. The yields include statistical uncertainties due to the  Monte Carlo (MC) samples and systematic uncertainties as described in Table \ref{tth-table}.

@@

\pagebreak
%The fake rate corresponds to non-prompt leptons.% Non prompt leptons are leptons that passed the selection, and usually comes from decays from b-jets (hadronized quarks). But due to jet signature is reconstructed as leptons, some particular signatures or errors in reconstruction, passed as leptons and then they called fakes leptons. Rare SM is a group of other processes: t$\bar{t}$t$\bar{t}$,WWW,WWZ,WZZ,WW,$t$Zq. Due to low number of events, they grouped the events as one histogram. 
\section{Multivariable discriminant}
Due to small signal to background ratio caused by the small cross section of $tH$, a multivariable discriminant, which separates signal from backgrounds, is necessary to optimize the signal sensitivity. The multivariable discriminant is a Boosted Decision Tree (BDT) that takes a set of input features and splits input data recursively based on those features\cite{tmva}. The features can be a mix of categorical and continuous data.
The BDT training is performed using several event variables.
In this analysis, the BDT discriminant was trained to discriminate against $t\bar{t}V$ background, because this background is one of the largest backgrounds. The variables used for the BDT were the following:

### 2019-11-25 tesis_hiram/Chapter4/chapter4.tex
b

		\begin{figure}[ht]
		\centering
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/simple.png}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/simple-kt-1.png}
		\end{minipage}
		\caption[Post-fit Signal and Backgrounds for $tH$ process]{Post-fit signal and background yields for $tH$ process for SM (Left) and $k_t=-1$ (Right).
			%In the box below each distribution, the ratio of the observed and predicted event yields is shown
		}
		\label{simple}
	\end{figure}
	\begin{table}[ht]
		\centering
		\caption[Postfit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$]{Postfit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
		\begin{tabular}{ccc}
			\hline
			Process & SM & $k_{t}$=-1 \\
			\hline
			$t\bar{t}W$ & 68$\pm$8.9& 68 $\pm$8.9 \\
			$t\bar{t}Z$ & 25.9$\pm$3.8&25.9$\pm$3.8\\
			$WZ$ & 15.1$\pm$7.4& 15.1$\pm$7.4\\
			Rares & 20.8$\pm$4.8& 20.8$\pm$4.8 \\
			Fakes & 80.9$\pm$9.0& 80.9$\pm$8.9 \\
			$t\bar{t}H$ & 24.2$\pm$2.0 & 24.2$\pm$2.0 \\
			\hline
			$tH$& 2.1$\pm$16.5 &26.2$\pm$13.1 
		\end{tabular}
		\label{table1}
	\end{table}
	\begin{table}[ht!]
		\small
		\centering
		\caption{$\alpha$ and $\mu$ values for the fit to Asimov data corresponding to 35.9 fb $^{-1}$}
		\begin{tabular}{ccc}
			\hline
			Parameter & SM &$k_t$=-1\\
			\hline
			$\mu$ & 1.00 $\pm$ 7.74& 1.0 $\pm$ 0.5\\
			$\alpha_{t\bar{t}W}$& 0.00 $\pm$ 0.89& 0.00 $\pm$ 089\\
			$\alpha_{t\bar{t}Z}$ & 0.00 $\pm$ 0.98& 0.00 $\pm$ 0.98\\
			$\alpha_{WZ}$ & 0.00 $\pm$ 0.97& 0.00 $\pm$ 0.97\\
			$\alpha_{Rares}$ &0.00 $\pm$ 0.95&0.00 $\pm$ 0.98 \\
			$\alpha_{Fakes}$ & 0.00 $\pm$ 0.96& 0.00 $\pm$ 0.95\\
			$\alpha_{t\bar{t}H}$ &0.00 $\pm$ 0.98& 0.00 $\pm$ 0.98\\
		\end{tabular}
		\label{parameters}
	\end{table}

@@

In order to find the upper limit value of $\mu$, we search for the largest value of $\mu$ such that $q$ remains below the shaded region shown in figure \ref{chi}, where $\alpha$=0.05 in this case. It is useful to scan $q$ as function of $\mu$, which is normally a parabolic function as shown in figure \ref{scanl}. In the SM case, the scan has a wider shape in comparison to the $k_t$=-1. This is due to larger statistical uncertainty on the $\mu$ parameter. 
	Using the above technique, we find an expected upper limit $\mu < $17.0 for SM model and $\mu < $ 2.3 for $k_t$=-1 model. 
		\begin{figure}[ht]
		\centering
		\begin{minipage}[b]{0.49\textwidth}
			\includegraphics[width=\textwidth,height=0.31\textheight]{Chapter4/Likelihood.png}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.49\textwidth}
			\includegraphics[width=\textwidth,height=0.31\textheight]{Chapter4/Likelihood-kt-1.png}
		\end{minipage}
		\caption[Likelihood scan for SM and $k_t$=-1]{Likelihood scan for SM (Left) and $k_t$=-1 (Right).}
		\label{scanl}
	\end{figure}
	\pagebreak
	%%sigma son las probabilidades que corresponden a 1sigma=68, 2sigma=95, 3sigma=98 y sigma son los limites de la integral de una gaussiana
	\section{Extrapolation to higher luminosity}
	In the past section, it was shown that the signal strength with an integrated luminosity of 35.9 fb$^{-1}$ is not significant. The LHC has already collected data for integrated luminosity of 150 fb$^{-1}$ for run 2 which finished in 2018. Run 3 starts in 2021 and is expected an integrated luminosity of 300fb$^{-1}$ and for the high luminosity phase of LHC, expected to collect 3000 fb$^{-1}$. Therefore, it is interesting to study the sensitivity of the signal strength at higher luminosity. 
	An extrapolation (scale) is applied to the Asimov data and the statistical uncertainty is adjusted accordingly. For this analysis we assume the systematic uncertainties assigned to the background are the same.

	In figure \ref{hm}, an estimated prediction of the signal and background events for higher luminosity is shown. As the luminosity increases, the number of events for both signal and backgrounds also increases, as previously explained in Chapter 1. But even with the increase of number of events, the statistical uncertainty of the data is too large with respect to the expected signal. In the likelihood scan for higher luminosity, as the luminosity increases, the relative uncertainty on the signal strength $\mu$ decreases. This is caused by the increased events available for the fit.

	The same method is used for the model $k_t$=-1 in figure \ref{hm1}. In this case, the number of events for the signal is more appreciable in comparison with the SM model. However, the likelihood scan parabolas are very closed and that indicates a decrease in the uncertainty of $\mu$ more notable than SM case. 
	Of course, as the previous section, we estimate the upper limit for these cases and they are shown in the Table \ref{upper}

@@

	\begin{figure}[ht]
		\centering
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/150fb/simple-150.png}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.5\textwidth}
			\includegraphics[width=\textwidth,height=0.31\textheight]{Chapter4/150fb/Likelihood.png}
		\end{minipage}
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/300fb/simple-300.png}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.5\textwidth}
			\includegraphics[width=\textwidth,height=0.31\textheight]{Chapter4/300fb/Likelihood.png}
		\end{minipage}
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/3000fb/simple-3000.png}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.5\textwidth}
			\includegraphics[width=\textwidth,height=0.31\textheight]{Chapter4/3000fb/Likelihood.png}
		\end{minipage}
		\caption{Fit and likelihood scan for 150 fb$^{-1}$, 300 fb$^{-1}$ and 3000 fb$^{-1}$ in SM model.}
		\label{hm}
	\end{figure}
	\pagebreak

>>>>

		\begin{figure}[ht]
		\centering
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/simple.png}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/simple-kt-1.png}
		\end{minipage}
		\caption[Post-fit Signal and Backgrounds for $tH$ process]{Post-fit signal and background yields for $tH$ process for SM (Left) and $k_t=-1$ (Right).
			%In the box below each distribution, the ratio of the observed and predicted event yields is shown
		}
		\label{simple}
	\end{figure}
	\begin{table}[ht]
		\centering
		\caption[Post-fit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$]{Post-fit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
		\begin{tabular}{ccc}
			\hline
			Process & SM & $k_{t}$=-1 \\
			\hline
			$t\bar{t}W$ & 68$\pm$8.9& 68 $\pm$8.9 \\
			$t\bar{t}Z$ & 25.9$\pm$3.8&25.9$\pm$3.8\\
			$WZ$ & 15.1$\pm$7.4& 15.1$\pm$7.4\\
			Rares & 20.8$\pm$4.8& 20.8$\pm$4.8 \\
			Fakes & 80.9$\pm$9.0& 80.9$\pm$8.9 \\
			$t\bar{t}H$ & 24.2$\pm$2.0 & 24.2$\pm$2.0 \\
			\hline
			$tH$& 2.1$\pm$16.5 &26.2$\pm$13.1 
		\end{tabular}
		\label{table1}
	\end{table}
	\begin{table}[ht!]
		\small
		\centering
		\caption{$\alpha$ and $\mu$ values for the fit to Asimov data corresponding to 35.9 fb $^{-1}$}
		\begin{tabular}{ccc}
			\hline
			Parameter & SM &$k_t$=-1\\
			\hline
			$\mu$ & 1.00 $\pm$ 7.74& 1.0 $\pm$ 0.5\\
			$\alpha_{t\bar{t}W}$& 0.00 $\pm$ 0.89& 0.00 $\pm$ 089\\
			$\alpha_{t\bar{t}Z}$ & 0.00 $\pm$ 0.98& 0.00 $\pm$ 0.98\\
			$\alpha_{WZ}$ & 0.00 $\pm$ 0.97& 0.00 $\pm$ 0.97\\
			$\alpha_{Rares}$ &0.00 $\pm$ 0.95&0.00 $\pm$ 0.98 \\
			$\alpha_{Fakes}$ & 0.00 $\pm$ 0.96& 0.00 $\pm$ 0.95\\
			$\alpha_{t\bar{t}H}$ &0.00 $\pm$ 0.98& 0.00 $\pm$ 0.98\\
		\end{tabular}
		\label{parameters}
	\end{table}

@@

In order to find the upper limit value of $\mu$, we search for the largest value of $\mu$ such that $q$ remains below the shaded region shown in Figure \ref{chi}, where $\alpha$=0.05 in this case. It is useful to scan $q$ as function of $\mu$, which is normally a parabolic function as shown in Figure \ref{scanl}. In the SM case, the scan has a wider shape in comparison to the $k_t$=-1. This is due to larger statistical uncertainty on the $\mu$ parameter. 
	Using the above technique, we find an expected upper limit $\mu < $17.0 for SM model and $\mu < $ 2.3 for $k_t$=-1 model. 
		\begin{figure}[ht]
		\centering
		\begin{minipage}[b]{0.49\textwidth}
			\includegraphics[width=\textwidth,height=0.31\textheight]{Chapter4/Likelihood.png}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.49\textwidth}
			\includegraphics[width=\textwidth,height=0.31\textheight]{Chapter4/Likelihood-kt-1.png}
		\end{minipage}
		\caption[Likelihood scan for SM and $k_t$=-1]{Likelihood scan for SM (Left) and $k_t$=-1 (Right).}
		\label{scanl}
	\end{figure}
	\pagebreak
	%%sigma son las probabilidades que corresponden a 1sigma=68, 2sigma=95, 3sigma=98 y sigma son los limites de la integral de una gaussiana
	\section{Extrapolation to higher luminosity}
	In the past section, it was shown that the signal strength with an integrated luminosity of 35.9 fb$^{-1}$ is not significant. The LHC has already collected data for integrated luminosity of 150 fb$^{-1}$ for run 2 which finished in 2018. Run 3 starts in 2021 and is expected an integrated luminosity of 300fb$^{-1}$ and for the high luminosity phase of LHC, expected to collect 3000 fb$^{-1}$. Therefore, it is interesting to study the sensitivity of the signal strength at higher luminosity. 
	An extrapolation (scale) is applied to the Asimov data and the statistical uncertainty is adjusted accordingly. For this analysis we assume the systematic uncertainties assigned to the background are the same.

	In Figure \ref{hm}, an estimated prediction of the signal and background events for higher luminosity is shown. As the luminosity increases, the number of events for both signal and backgrounds also increases, as previously explained in Chapter 1. But even with the increase of number of events, the statistical uncertainty of the data is too large with respect to the expected signal. In the likelihood scan for higher luminosity, as the luminosity increases, the relative uncertainty on the signal strength $\mu$ decreases. This is caused by the increased events available for the fit.

	The same method is used for the model $k_t$=-1 in Figure \ref{hm1}. In this case, the number of events for the signal is more appreciable in comparison with the SM model. However, the likelihood scan parabolas are very closed and that indicates a decrease in the uncertainty of $\mu$ more notable than SM case. 
	Of course, as the previous section, we estimate the upper limit for these cases and they are shown in the Table \ref{upper}

@@

	\begin{figure}[ht]
		\centering
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/150fb/simple-150.png}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.5\textwidth}
			\includegraphics[width=\textwidth,height=0.31\textheight]{Chapter4/150fb/Likelihood.png}
		\end{minipage}
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/300fb/simple-300.png}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.5\textwidth}
			\includegraphics[width=\textwidth,height=0.31\textheight]{Chapter4/300fb/Likelihood.png}
		\end{minipage}
		\begin{minipage}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{Chapter4/3000fb/simple-3000.png}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.5\textwidth}
			\includegraphics[width=\textwidth,height=0.31\textheight]{Chapter4/3000fb/Likelihood.png}
		\end{minipage}
		\caption{Fit and likelihood scan for 150 fb$^{-1}$, 300 fb$^{-1}$ and 3000 fb$^{-1}$ in SM}
		\label{hm}
	\end{figure}
	\pagebreak
